Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-06-03 manuscript-chicago.Rmd
More quote formatting

>a religious or linguistic minority
might suffer disproportionately in a given society, and this form of
aggrievement can lead to unrest across the social lines that distinguish the
minority group. Therefore, while collective cohesion is a function of targeted
maldistributions, it is individual penury that allows for this collective
mobilization. [@regan2005greed]

>>>>

\noindent a religious or linguistic minority
might suffer disproportionately in a given society, and this form of
aggrievement can lead to unrest across the social lines that distinguish the
minority group. Therefore, while collective cohesion is a function of targeted
maldistributions, it is individual penury that allows for this collective
mobilization.
